\documentclass[]{kyvernitis-resume}
\fullname{Gearoid
 O'Treasaigh}
\jobtitle{Software Craftsmanship Coach}

\begin{document}
\resumeheader
{\linkedin{gearoid-o-treasaigh}}
{\email{gearoid9@gmail.com}}
{\github{gotreasa}}
{\phone{+44 78-2690-4551}}
{\website{gearoid.otreasaigh.com}}
{\nationality{Ireland}}
{\address{Surbiton, London, United Kingdom}}

\begin{section}{Accomplishments}
 \begin{subsectionaccomplishment}{Technical Skills Transformation}
	 \item {Led an organisation transformation of 1000 developers across London, Brazil and Mexico. Trained dojos on eXtreme Programming practices.
	             Improved participants TDD, planning, and DevOps skills which improved their teams DORA scores.}
	 \item {Created a course on basic data analysis using Jupyter Notebooks which enabled both
	             technical and non-technical participants to make more informed decsions building their applications.
	             This improved their ability to build the right features for users.}
	 \item {Organised outward mindset classes and a guild for an oganisation of over 260 people
	             which had an impact on teams ability to focus on outcome and achieve their OKRs.}
	 \item Received the "Peer-to-Peer Recognition - Growth Minded" award for transforming the organisation.
 \end{subsectionaccomplishment}

 \begin{subsectionaccomplishment}{Mastering the Art of Excuse-Making}
	 \item{Explored the art of crafting creative and believable excuses for missed deadlines and unfinished work. Special emphasis was given to the power of plausible deniability, feigning technical difficulties, and perfecting the "dog ate my homework" alibi.}
 \end{subsectionaccomplishment}

 \begin{subsectionaccomplishment}{DevOps Transformation}
	 \item Transformed the deployment process for an on-premise instance which took an seventy two to be able to run within a couple of hours.
	 \item Continuously sought areas that were not automated and led the team to be able to transform and automate the deployments.
	 \item Received an Outstanding Technical Achievement Award for being the first team to introduce Urban Code Deployment and using it to deploy to production.
 \end{subsectionaccomplishment}

\end{section}

\begin{section}{Work Experience}
 \begin{subsection}{IBM}{Software Craftsmanship Coach}{January 2022 -- Present}{London, United Kingdom}
	 \item Trained 4 developer dojos on eXtreme Programming practices.
	 Improved participants TDD, planning, and DevOps skills which improved their teams DORA scores.
	 \item Created a course on basic data analysis using Jupyter Notebooks which enabled both
	 technical and non-technical participants to make more informed decsions building their applications.
	 This improved their ability to build the right features for users.
	 \item Organised outward mindset classes and a guild for an oganisation of over 260 people which had an impact on teams ability to focus on outcome and achieve their OKRs.
	 \item Received the "Peer-to-Peer Recognition - Growth Minded" award for transforming the organisation.
 \end{subsection}

 \begin{subsection}{IBM}{Implementation Architect \& Technical Lead}{October 2020 -- December 2021}{London, United Kingdom}
	 \item Architected and led the development of the migration from a custom NodeJS application to Salesforce, enabling 200k users to migrate seamlessly to Salesforce.
	 \item Designed the microservices used as part of Salesforce for partner relationship management.
 \end{subsection}

 \begin{subsection}{IBM}{Senior JavaScript Full Stack Development Lead}{May 2019 -- October 2020}{London, United Kingdom}
	 \item Transformed the software deal registration process which lead to an increase in the NPS score and ensured the entire process was automated within the NodeJS application.
	 \item Mentored a group of 3 development leads in squad leadership and agile refinement.
	 \item Led and mentored a tribe of 18 developers.
 \end{subsection}

 \begin{subsection}{IBM}{JavaScript Full Stack Development Lead}{January 2017 -- May 2019}{Dublin, Ireland}
	 \item Created a NodeJS application that automated opportunity, incentive and deal registration creation for 10k business partners and their 200k users.
	 \item The transformation lead to users instantly recording the opportunities and products that they were selling from an old process that could take them days as they waited for each step to complete.
	 \item Led a team of 6 people as part of the agile tribe.
	 \item Earned an Outstanding Technical Achievement award for the application.
 \end{subsection}

 \begin{subsection}{IBM}{DevOps \& Web Development Lead}{March 2011 -- January 2017}{Dublin, Ireland}
	 \item Transformed the deployment process for an on-premise instance which took an seventy two to be able to run within a couple of hours.
	 \item Continuously sought areas that were not automated and led the team to be able to transform and automate the deployments.
	 \item Received an Outstanding Technical Achievement Award for being the first team to introduce Urban Code Deployment and using it to deploy to production.
 \end{subsection}

 \begin{subsectionnolist}{IBM}{Web Developer}{May 2009 -- March 2011}{Dublin, Ireland}
 \end{subsectionnolist}

 \begin{subsectionnolist}{IBM}{Web Application Graduate}{June 2008 -- May 2009}{Dublin, Ireland}
 \end{subsectionnolist}

\end{section}

\sectiontable{Technical skills}{
	\entry{Programming Languages}{JavaScript, Java, Python, Bash, HTML, CSS}
	\entry{eXtreme Programming}{Pair Programming, Test Driven Development, Behaviour Driven Development, DevOps, CI/CD}
	\entry{Software Engineering}{Agile, Architecture, Git, Docker}
}

\sectiontable{Awards}{
	\entry{Peer-to-Peer Recognition - Growth Minded}{\hfill \textit{May 2023}}
	\entry{IBM Service Corps}{\hfill \textit{August 2018}}
	\entry{Outstanding Technical Achievement}{\hfill \textit{August 2017}}
	\entry{Outstanding Technical Achievement}{\hfill \textit{November 2014}}
	\entry{People's Innovation Choice}{\hfill \textit{October 2014}}
	\entry{Leadership Excellence}{\hfill \textit{November 2013}}
}

\sectiontable{Soft skills}{
	\entry{Coaching}{Professional coaching one on one and training new coaches. }
	\entry{Leadership}{Leading transformation initiatives and technical lead for 3 squads.}
	\entry{Trainer}{Running experiental training using training from the back of the room techniques.}
}

\sectiontable{Certifications}{
	\entry{Agile Coaching}{ICAgile \hfill \textit{June 2023}}
	\entry{Agile Team Facilitation}{ICAgile \hfill \textit{June 2023}}
	\entry{IBM Garage Foundation}{IBM \hfill \textit{April 2023}}
	\entry{Slack Certified Admin}{Slack \hfill \textit{April 2023}}
	\entry{XP Farm Coach}{IBM \hfill \textit{March 2023}}
	\entry{IBM Career Coach}{IBM \hfill \textit{November 2022}}
	\entry{Blue Core Coaching Supervisor}{IBM \hfill \textit{October 2022}}
	\entry{Developing and Implementing an Outward Mindset}{Arbinger Institute \hfill \textit{February 2022}}
	\entry{Blue Core Coach}{IBM \hfill \textit{June 2019}}
}

\begin{section}{Education}
 \begin{subsectionnobullet}{Bachelor of Science}{Honours BSc, Computing Studies}{University of Galway}{September 2004 -- June 2008}
	 \italicitem{Thesis: Porting pkgsrc from NetBSD to MINIX}
	 \italicitem{Final Grade: 1:1}
 \end{subsectionnobullet}
\end{section}

\end{document}
