\section[\faGears]{Work history}
\job{01/2022 - Present}
{IBM, London, United Kingdom}
{Technical Agile Coach}
{\begin{itemize}
		\item Trained 4 developer dojos on eXtreme Programming practices.
		      Improved participants TDD, planning, and DevOps skills which improved their teams DORA scores.
		\item Created a course on basic data analysis using Jupyter Notebooks which enabled both
		      technical and non-technical participants to make more informed decsions building their applications.
		      This improved their ability to build the right features for users.
		\item Organised outward mindset classes and a guild for an oganisation of over 260 people which had an impact on teams ability to focus on outcome and achieve their OKRs.
		\item Received the Peer-to-Peer recognition for transforming the organisation.
	\end{itemize}}
\job{10/2020 - 12/2021}
{IBM, London, United Kingdom}
{Implementation Architect & Technical \newline
	Lead}
{\begin{itemize}
		\item Architected and led the development of the migration from a custom NodeJS application to Salesforce, enabling 200k users to migrate seamlessly to Salesforce.
		\item Designed the microservices used as part of Salesforce for partner relationship management.
	\end{itemize}}
\job{05/2019 - 10/2020}
{IBM, London, United Kingdom}
{Senior JavaScript Full Stack \newline
	Development Lead}
{\begin{itemize}
		\item Transformed the software deal registration process which lead to an increase in the NPS score and ensured the entire process was automated within the NodeJS application.
		\item Mentored a group of 3 development leads in squad leadership and agile refinement.
		\item Led and mentored a tribe of 18 developers.
	\end{itemize}}
\job{01/2017 - 04/2019}
{IBM, Dublin, Ireland}
{JavaScript Full Stack \newline
	Development Lead}
{\begin{itemize}
		\item Created a NodeJS application that automated opportunity, incentive and deal registration creation for 10k business partners and their 200k users.
		\item The transformation lead to users instantly recording the opportunities and products that they were selling from an old process that could take them days as they waited for each step to complete.
		\item Led a team of 6 people as part of the agile tribe.
		\item Earned an Outstanding Technical Achievement award for the application.
	\end{itemize}}
\job{03/2011 - 12/2016}
{IBM, Dublin, Ireland}
{DevOps and Web Development \newline
	Lead}
{\begin{itemize}
		\item Transformed the deployment process for an on-premise instance which took an seventy two to be able to run within a couple of hours.
		\item Continuously sought areas that were not automated and led the team to be able to transform and automate the deployments.
		\item Received an Outstanding Technical Achievement Award for being the first team to introduce Urban Code Deployment and using it to deploy to production.
	\end{itemize}}
\job{05/2009 - 03/2011}
{IBM, Dublin, Ireland}
{Web Developer}
{}
\job{06/2008 - 05/2009}
{IBM, Dublin, Ireland}
{Web Application Graduate}
{}